---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
/* General body styling */
body {
  font-family: Arial, sans-serif;
  color: #333;
  background-color: #f7f7f7;
  margin: 20px;
}

/* Header styling */
h1, h2, h3 {
  color: #2c3e50;
  font-weight: bold;
  text-align: center;
}

/* Section titles (h2) */
h2 {
  border-bottom: 2px solid #2c3e50;
  padding-bottom: 5px;
  margin-bottom: 15px;
}

/* Paragraph text */
p {
  font-size: 14px;
  line-height: 1.6;
  margin-bottom: 15px;
  text-align: justify;
}

/* Table styling */
table {
  width: 100%;
  border-collapse: collapse;
  margin-top: 20px;
}

table, th, td {
  border: 1px solid #ddd;
}

th, td {
  padding: 8px;
  text-align: left;
}

th {
  background-color: #f2f2f2;
}

/* Plot size adjustment */
img {
  max-width: 100%;
  height: auto;
  display: block;
  margin: 0 auto;
}

```

##  YouTube Advertisement Analysis

This report tracks and analyzes YouTube advertisements, focusing on key variables such as the type of advertisements shown (Ad_Type), the length of advertisements shown (Ad_Length), whether individuals choose to skip the advertisements (Ad_Skipped) and the engagement levels of the advertisements to be (Ad_Engaged). The goal is to provide insights into how different advertisement types and characteristics influence viewer engagement and interaction, helping to understand ad performance across various metrics.


```{r, echo=FALSE}
library(tidyverse)

logged_data  <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQQSF3f45kWWR-spYlDLPZ6OOXZuDwSaTNyutQWj_ej8fKHdr9RE--fnIKmUCvDPugwLdZa9J3Dbb_1/pub?gid=2013861753&single=true&output=csv")


    latest_data <- logged_data %>%
      rename(
        Ad_Type = 'What type of ad did you encounter?',
        Ad_Length = 'How long was the Advertisment?',
        Ad_Skipped = 'Did you skip the advetisment?',
        Ad_Engaged = 'How engaging was the advertisment?'
      )

# New data frame between Ad type and their engagement
Ad_TE <- latest_data %>%
  select(Ad_Type, Ad_Engaged)

# New data frame between Ad length and their engagement
Ad_LE <- latest_data %>%
  select(Ad_Length, Ad_Engaged)

# New data frame between Ad length and their engagement
Ad_TL <- latest_data %>%
  select(Ad_Type, Ad_Length)

```


```{r, echo=FALSE}
# Bar chart for Ad_Type (count of ad types)
ggplot(latest_data, aes(x = Ad_Type)) +
  geom_bar(fill = "springgreen") +
  labs(title = "Ad Types", x = "Ad Type", y = "Count")

# Bar chart for Skipped_Ad (count of whether users skipped the ad)
ggplot(latest_data, aes(x = Ad_Skipped)) +
  geom_bar(fill = "slategrey") +
  labs(title = "Ad Skipping Behavior",
       x = "Skipped Ad",
       y = "Count"
  )
```

**Mean Ad Length:** `r round(mean(latest_data$Ad_Length), 2)` seconds  
**Median Ad Length:** `r round(median(latest_data$Ad_Length), 2)` seconds

```{r, echo=FALSE}

# Scatter plot: Ad length and Ad Type
ggplot(Ad_TL, aes(y = Ad_Length, x = Ad_Type)) +
  geom_point(color = "cadetblue", size = 3) +
  labs(
    title = "Relationship between Ad Length and Ad Type",
    x = "Ad Type",
    y = "Ad Length (seconds)"
  )
```

**Average Engagement Score:** `r round(mean(Ad_TE$Ad_Engaged), 2)`  
**Most Frequent Engagement Score:** `r as.numeric(names(sort(table(Ad_TE$Ad_Engaged), decreasing = TRUE))[1])`

```{r, echo=FALSE}
# Bar chart: Distribution of Ad Engagement (on a 1-5 scale)
print(engagement_chart <- ggplot(Ad_TE, aes(x = factor(Ad_Engaged))) +
  geom_bar(fill = "orange") +
  labs(
    title = "Ad Engagement",
    x = "Engagement (1-5)",
    y = "Count",
  ))

mean_E_T <- latest_data %>%
  group_by(Ad_Type) %>%
  summarise(mean_engagement = mean(Ad_Engaged))
```

The mean engagement score for **Health and Wellbeing Advertisments** is `r round(mean_E_T$mean_engagement[mean_E_T$Ad_Type == "Health and Wellbeing Advertisments"], 2)`.

The mean engagement score for **Product Advertisment** is `r round(mean_E_T$mean_engagement[mean_E_T$Ad_Type == "Product Advertisment (Clothing, Food, etc)"], 2)`.

The mean engagement score for **Service Advertisement** is `r round(mean_E_T$mean_engagement[mean_E_T$Ad_Type == "Service Advertisment (Streaming Platforms, etc)"], 2)`.


```{r, echo=FALSE}

# Scatter plot: Ad Engagement and Ad Type
ggplot(Ad_TE, aes(y = Ad_Engaged, x = Ad_Type)) +
  geom_point(color = "coral3", alpha = 0.5, size = 2) +
  labs(
    title = "Relationship between Ad engagement and Ad Type",
    x = "Ad Type",
    y = "Ad Engagememt (1-5)"
  )

# Scatter plot between Ad Length and Ad Engaged
ggplot(Ad_LE, aes(x = Ad_Length, y = Ad_Engaged)) +
  geom_point(color = "slateblue4", alpha = 0.5, size = 2) +  
  labs(
    title = "Ad engagment based on length",
    x = "Ad Length (seconds)",
    y = "Ad Engagement (1-5)",
  )
```